My title

### 2024-03-19 paper/paper.qmd
Issue resolved!! Graphs are now rendering properly!!! Yay:)

@@

//Graph of Education level and opinions for gun permits

@@

//Graph of MaleVsFemale
```{r,echo=FALSE, results=FALSE}
#| echo: false
#| warning: false
#| message: false   
#2    GGPlot for GenderAndGunPermit
## load in CSV ##

@@

### turn strings into numbers
transform(GenderAndGunPermit, 'Female' = as.numeric('Female')) 
transform(GenderAndGunPermit, 'Male' = as.numeric('Male'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)

###### MAKE THE PLOT #######
ggplot(data=GenderAndGunPermit, aes(x = Year, y=Total, group = Gender)) +
  geom_line(aes(colour=Gender))+
  labs(title = "Percentage of American Women vs Men \n in favour of police backed gun permits", y = "Total % in favour")

@@

@@

### turn strings into numbers
transform(RaceAndGunlaw, 'White' = as.numeric('White')) 
transform(RaceAndGunlaw, 'Black' = as.numeric('Black')) 
transform(RaceAndGunlaw, 'Other' = as.numeric('Other'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)

###### MAKE THE PLOT #######
ggplot(data=RaceAndGunlaw, aes(x = Year, y=Total, group = Race)) +
  geom_line(aes(colour=Race))+
  labs(title = "Americans in favour of police backed \n gun permits based on racial identity", y = "Total % in favour")

@@

TESTING GROUND

```{r}
### Load required libraries
library(ggplot2)
library(tidyr)

```{r}

#2    GGPlot for GenderAndGunPermit
## load in CSV ##

### turn strings into numbers
transform(GenderAndGunPermit, 'Female' = as.numeric('Female')) 
transform(GenderAndGunPermit, 'Male' = as.numeric('Male'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)

###### MAKE THE PLOT #######
ggplot(data=GenderAndGunPermit, aes(x = Year, y=Total, group = Gender)) +
  geom_line(aes(colour=Gender))+
  labs(title = "Percentage of American Women vs Men \n in favour of police backed gun permits", y = "Total % in favour")

>>>>

## load in CSV ##

# Plot 1: GGPlot for GunLaw
GunlawRepVsDem.csv <- read_csv(here("./data/analysis_data/GunlawRepVsDem.csv"))
transform(GunlawRepVsDem.csv, 'Total Americans in Favour' = as.numeric('Total Americans in Favour'))

### turn strings into numbers
transform(GunlawRepVsDem.csv, 'Democrats' = as.numeric('Democrats')) 
transform(GunlawRepVsDem.csv, 'Republicans' = as.numeric('Republicans')) 
transform(GunlawRepVsDem.csv, 'Other/Non-affiliated' = as.numeric('Other/Non-affiliated'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)
GunlawRepVsDem.csv <- GunlawRepVsDem.csv |> 
  pivot_longer(cols=c('Democrats', 'Republicans', 'Other/Non-affiliated'), names_to='Party', values_to='Total')
###### MAKE THE PLOT #######
ggplot(data=GunlawRepVsDem.csv, aes(x = Year, y=Total, group = Party)) +
  geom_line(aes(colour=Party))+
  labs(title = "Americans in favour of police backed gun permits \n based on political affiliation", y = "Total % in favour")

@@

//Graph of Education level and opinions for gun permits
```{r,echo=FALSE, results=FALSE}
#| echo: false
#| warning: false
#| message: false   
#3    GGPlot for GunlawHighestDegree

## load in CSV ##
GunlawHighestDegree.csv <- read_csv(here("./data/analysis_data/GunlawHighestDegree.csv"))
transform(GunlawHighestDegree.csv, 'Total Americans in Favour' = as.numeric('Total Americans in Favour'))

### turn strings into numbers
transform(GunlawHighestDegree.csv, 'Degree or Higher' = as.numeric('Degree or Higher')) 
transform(GunlawHighestDegree.csv, 'Highschool' = as.numeric('Highschool')) 
transform(GunlawHighestDegree.csv, 'No Highschool' = as.numeric('No Highschool'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)
GunlawHighestDegree.csv <- GunlawHighestDegree.csv |> 
  pivot_longer(cols=c('Degree or Higher', 'Highschool', 'No Highschool'), names_to='Education', values_to='Total')
###### MAKE THE PLOT #######
ggplot(data=GunlawHighestDegree.csv, aes(x = Year, y=Total, group = Education)) +
  geom_line(aes(colour=Education))+
  labs(title = "Percentage of Americans in favour of police \n backed gun permits based on higest level of education", y = "Total % in favour")

@@

//Graph of MaleVsFemale
```{r,echo=FALSE, results=FALSE}
#| echo: false
#| warning: false
#| message: false   
#2    GGPlot for GenderAndGunPermit
## load in CSV ##
GenderAndGunPermit.csv <- read_csv(here("./data/analysis_data/GenderAndGunPermit.csv"))
transform(GenderAndGunPermit.csv, 'Total Americans in Favour' = as.numeric('Total Americans in Favour'))

@@

### turn strings into numbers
transform(GenderAndGunPermit.csv, 'Female' = as.numeric('Female')) 
transform(GenderAndGunPermit.csv, 'Male' = as.numeric('Male'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)
GenderAndGunPermit.csv <- GenderAndGunPermit.csv |> 
  pivot_longer(cols=c('Female', 'Male'), names_to='Gender', values_to='Total')
###### MAKE THE PLOT #######
ggplot(data=GenderAndGunPermit.csv, aes(x = Year, y=Total, group = Gender)) +
  geom_line(aes(colour=Gender))+
  labs(title = "Percentage of American Women vs Men \n in favour of police backed gun permits", y = "Total % in favour")

@@

#5    GGPlot for RaceAndGunlaw

## load in CSV ##
RaceAndGunlaw.csv <- read_csv(here("./data/analysis_data/RaceAndGunlaw.csv"))
transform(RaceAndGunlaw.csv, 'Total Americans in Favour' = as.numeric('Total Americans in Favour'))

@@

### turn strings into numbers
transform(RaceAndGunlaw.csv, 'White' = as.numeric('White')) 
transform(RaceAndGunlaw.csv, 'Black' = as.numeric('Black')) 
transform(RaceAndGunlaw.csv, 'Other' = as.numeric('Other'))

####Make 2 columns side by side into two values in one column one above the other (turn data into long format)
RaceAndGunlaw.csv <- RaceAndGunlaw.csv |> 
  pivot_longer(cols=c('White', 'Black', 'Other'), names_to='Race', values_to='Total')
###### MAKE THE PLOT #######
ggplot(data=RaceAndGunlaw.csv, aes(x = Year, y=Total, group = Race)) +
  geom_line(aes(colour=Race))+
  labs(title = "Americans in favour of police backed \n gun permits based on racial identity", y = "Total % in favour")

@@
